Initial Analysis

### 2019-08-30 Initial_Analysis.Rmd
updated EstNeighFun for faster processing

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
#The File
fnam_world <- "SAUEEZ_July2015.shp"
#Load it!

World_EEZs <- readOGR(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

#### Grid cell information ####

@@

>>>>

  # Get sparse matrix
  int = suppressMessages(st_intersects(Shapefile))
  # Warnning message
  # although coordinates are longitude/latitude, st_intersects assumes that they are planar

  # Intitalize new object
  mat = NULL

  # Fill
  for(i in 1:NROW(int)){
    #Create matrix with ID and intersecting IDs
    tmp = cbind(i, int[[i]])

    # Join to Initalized object
    mat  = rbind(mat, tmp)
  }

  # Build final data.frame substituting ID for name (in this case nc$name)
  Result_table = data.frame(Name = Shapefile$Name[mat[,1]], 
                            Neighbor_Territory = Shapefile$Name[mat[,2]]
  )

  # Remove duplicates... eg of course an object intersects with itself...
  Result_table = Result_table[Result_table$Name != Result_table$Neighbor_Territory,]

  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbors_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

  )

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
#### Grid cell information ####

@@

### RFMO analysis

# Old code
```{r OLD_funEstNeighbors, eval = F, echo=T}
# Determine which countries are neighbors
